%-------------------------
% ATS-Optimized Resume for Ardi Rudini
% Tailored for: 3D Artist — Good Job Games
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%--- Custom commands ---
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ardi Rudini} \\ \vspace{1pt}
    \small +6285659001753 $|$ \href{mailto:ardirdeveloper@gmail.com}{\underline{ardirdeveloper@gmail.com}} $|$
    \href{https://www.linkedin.com/in/ardirdn/}{\underline{linkedin.com/in/ardirdn}} $|$
    \href{https://ardigamedev.com/}{\underline{ardigamedev.com}} $|$
    West Java, Indonesia
\end{center}


%-----------SUMMARY-----------
\section{Summary}
  \small{
    Passionate 3D Artist with over 7 years of experience creating clean, high quality 3D assets including environments, props, VFX, and animation for mobile games. Shipped 35 mobile games with 15 million combined downloads, working in close collaboration with 2D Concept artists, game designers, and developers to create great games played by millions of mobile gamers. Excellent command of 3D tools including Blender and Substance Painter, with excellent command of Adobe Creative Suite. Solid knowledge of modeling, lighting, color and composition. Passionate about mobile puzzle games and always driven by creativity, team spirit, and never-ending learning.
  }


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universitas Pembangunan Nasional Veteran Jakarta}{Jakarta, Indonesia}
      {Bachelor of Informatics}{September 2019 -- July 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Founder, Lead 3D Artist, and Level Designer}{September 2017 -- Present}
      {Trimatra Studio}{West Java, Indonesia}
      \resumeItemListStart
        \resumeItem{Created clean, high quality 3D assets including environments, props, VFX, and animation for 35 shipped mobile games across Google Play and Roblox, reaching 15 million combined downloads and visits.}
        \resumeItem{Created texture and UV maps for all game-ready 3D assets using Adobe Creative Suite (Photoshop), Substance Painter, and Blender, ensuring visual consistency and mobile optimization across multiple art styles.}
        \resumeItem{Created environmental concept models and plans, delivering optimized 3D assets with strict polygon budgets under 50,000 triangles per scene, achieving consistent 60 frames per second on low-end mobile devices.}
        \resumeItem{Worked in close collaboration with 2D Concept artists, game designers, and developers to create great games played by millions of mobile gamers, translating 2D concepts into clean, high quality 3D assets.}
        \resumeItem{Demonstrated solid knowledge of modeling, lighting, color and composition across 35 shipped titles, adapting to multiple art styles and visual directions while maintaining high quality standards.}
        \resumeItem{Led 3D art direction for Aku Si Juragan Empang (3.5 million downloads), creating environments, props, and character rigs with blend shapes, producing texture and UV maps, renders, and animation.}
        \resumeItem{Modeled, textured, and rigged 26 unique characters and 50 environment props for Juragan Fauna (100,000 downloads) using Adobe Creative Suite for texture creation and atlas textures for mobile rendering optimization.}
        \resumeItem{Constructed a cinematic open-world environment for Mount Nirwana on Roblox (7 million visits) using terrain sculpting, foliage instancing, and dynamic lighting, showcasing solid knowledge of lighting, color and composition.}
        \resumeItem{Prototyped over 30 hyper-casual and mobile puzzle games in partnership with Voodoo, soft-launching Beauty Race (500,000 plus downloads) after rigorous CPI testing and visual optimization for mobile platforms.}
        \resumeItem{Streamlined 3D assets and scenes to reduce crash rates by 40 percent on low-end mobile devices through draw call batching, texture atlasing, and multi-tier level of detail systems.}
        \resumeItem{Built custom 3D tools in Blender using Python that automated retopology, PBR texture baking, LOD generation, and export workflows, reducing per-asset production time from 30 minutes to under 3 minutes.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelance 3D Artist and Environment Designer}{February 2025 -- Present}
      {Fiverr}{Remote}
      \resumeItemListStart
        \resumeItem{Created clean, high quality 3D assets including environments, props, and VFX for client projects, working in close collaboration to translate concepts into production-ready 3D assets and reducing load times by 25 percent.}
        \resumeItem{Created texture and UV maps and environmental concept models for 5 gamification prototypes within two-week sprint cycles, adapting to each project's art style using 3D tools and Adobe Creative Suite.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Modular Character System and Pipeline} $|$ \emph{Blender, Substance Painter, Python}}{2024}
          \resumeItemListStart
            \resumeItem{Architected a modular character system with swappable body parts, creating clean, high quality 3D assets and enabling rapid generation of 100 unique character variations for mobile game production.}
            \resumeItem{Created texture and UV maps across all character variants using atlas texturing, packing material zones into single texture atlases to reduce per-character rendering cost by 45 percent on mobile devices.}
            \resumeItem{Built a Blender randomizer add-on in Python that automates character variant generation with LOD-aware toggling, reducing setup time by 80 percent.}
            \resumeItem{Integrated automatic level of detail generation across four tiers with customizable polygon reduction ratios for seamless visual transitions and optimized mobile performance.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Environment Art and Level Design Portfolio} $|$ \emph{Unreal Engine 5, Unity, Roblox Studio}}{2022 -- 2024}
          \resumeItemListStart
            \resumeItem{Created environmental concept models and plans for 12 complete environment scenes across Unreal Engine 5, Unity, and Roblox Studio in realistic and stylized art directions.}
            \resumeItem{Demonstrated solid knowledge of modeling, lighting, color and composition through cinematic lighting setups, terrain sculpting, and post-processing using Lumen Global Illumination, Nanite, and Material Editor.}
            \resumeItem{Created clean, high quality 3D assets including environments and props with GPU instanced rendering and distance-based detail levels, maintaining 60 frames per second on target hardware.}
            \resumeItem{Executed scene-level performance techniques including occlusion culling, draw call reduction, texture streaming, and mesh merging for optimized game-ready environments.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{BatchProcessPro Blender Add-on} $|$ \emph{Python, Blender API}}{2024}
          \resumeItemListStart
            \resumeItem{Designed a custom 3D tool automating retopology, PBR texture baking, LOD generation, rendering, and multi-file export, reducing total asset production time by 90 percent.}
            \resumeItem{Built an Auto Bake module for 6 PBR map types with automatic cage creation and material setup for game-engine-ready materials, compatible with Unity and Unreal Engine.}
            \resumeItem{Expanded the Auto LOD generator with customizable polygon reduction ratios and optional collider generation for mobile and console game engine export.}
            \resumeItem{Introduced Mask Map channel packing tools compatible with Unity HDRP, URP, and Unreal Engine ORM material formats.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{3D Tools:}{ Blender (Advanced), Substance Painter, Substance Designer, Modeling, Retopology, Mesh Optimization, Modular Asset Creation, Props, Characters, Environments, VFX} \\
     \textbf{Adobe Creative Suite:}{ Photoshop (Advanced), Illustrator, Texture Creation, Concept Art Support, Photo Manipulation, Image Compositing} \\
     \textbf{Texturing and UV:}{ Texture and UV Maps, Texture Painting, Material Setup, UV Mapping, UV Painting, Atlas Texturing, PBR Workflows, Hand-Painted Textures, Texture Compression} \\
     \textbf{Animation and Rigging:}{ Animation, Animation Keyframing, Character Rigging, Blend Shapes, Morph Targets, Skinning, Weight Painting} \\
     \textbf{Modeling, Lighting, Color and Composition:}{ Low-Poly Modeling, High-Poly Modeling, Cinematic Lighting, HDRI Lighting, Light Baking, Global Illumination, Color Theory, Composition, Visual Storytelling} \\
     \textbf{Game Engines:}{ Unity 2D and 3D, Unity HDRP and URP, Unreal Engine 5, Blueprints, Landscape Tools, Material Editor, Sequencer, Roblox Studio} \\
     \textbf{Mobile Optimization:}{ LOD Generation, Draw Call Batching, Occlusion Culling, Texture Streaming, GPU Profiling, Polygon Budget Management, Memory Optimization, Mobile Performance Profiling} \\
     \textbf{Environment Art:}{ Environmental Concept Models and Plans, Terrain Sculpting, Scene Layout, Lighting Design, World Building, Prop Placement, Blockout, Set Dressing} \\
     \textbf{Pipeline and Collaboration:}{ Python, Blender Plugins, Custom 3D Tools, Unity Editor Scripting, Automated Workflows, Close Collaboration, Cross-Functional Teamwork, Feedback and Transparency, Git, GitHub}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
