%-------------------------
% ATS-Optimized Resume for Ardi Rudini
% Tailored for: Technical Art Implementor — Tripledot Studios
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%--- Custom commands ---
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ardi Rudini} \\ \vspace{1pt}
    \small +6285659001753 $|$ \href{mailto:ardirdeveloper@gmail.com}{\underline{ardirdeveloper@gmail.com}} $|$
    \href{https://www.linkedin.com/in/ardirdn/}{\underline{linkedin.com/in/ardirdn}} $|$
    \href{https://ardigamedev.com/}{\underline{ardigamedev.com}} $|$
    West Java, Indonesia
\end{center}


%-----------SUMMARY-----------
\section{Summary}
  \small{
    Technical Artist and 3D Artist with over 7 years of experience implementing 3D and 2D art assets into Unity across 35 shipped mobile games with 15 million combined downloads. Skilled in the full Unity art pipeline including Canvas UI layout, Animator, Particle System, Shader Graph, and C\# editor scripting. Experienced in designing and implementing UI systems, user flows, wireframes, and design systems from scratch, ensuring visual consistency and seamless player experience. Proficient in Blender, Photoshop, Substance Painter, and Unity, with a strong eye for visual aesthetics and a track record of optimizing assets for performance without sacrificing quality. I have been making games for over 7 years and I still find it genuinely exciting. Working on a live title at Tripledot, where the work actually reaches millions of players every day, is exactly where I want to be.
  }


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universitas Pembangunan Nasional Veteran Jakarta}{Jakarta, Indonesia}
      {Bachelor of Informatics}{September 2019 -- July 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Founder, Lead 3D Artist, Technical Artist, and UI Designer}{September 2017 -- Present}
      {Trimatra Studio}{West Java, Indonesia}
      \resumeItemListStart
        \resumeItem{Implemented 3D and 2D art assets into Unity across 35 shipped mobile games, maintaining the original artistic vision while resolving technical issues that arose during asset integration and visual bug fixing.}
        \resumeItem{Designed and implemented functional UI layouts, animations, and tweens in Unity using Canvas and Animator, creating complete UI systems including user flows, wireframes, design systems, and UX patterns for every shipped title.}
        \resumeItem{Created visual effects using Unity Particle System and Shader Graph, producing responsive and polished in-game VFX including explosions, ambient particles, screen transitions, and feedback effects.}
        \resumeItem{Wrote Unity C\# editor scripts and custom Unity components to support the art team in implementing assets, automating repetitive tasks, and improving the asset pipeline to reduce implementation bottlenecks.}
        \resumeItem{Optimized 3D and 2D assets to achieve the best balance of visual quality and game performance, reducing crash rates by 40 percent on low-end devices through draw call batching, texture atlasing, and LOD systems.}
        \resumeItem{Handled asset management and support for the full art pipeline, maintaining organized project structures and ensuring all assets met technical requirements before submission for team review.}
        \resumeItem{Performed art and technical quality checks on all assets before delivery, identifying and fixing visual bugs and implementation issues with a keen eye for visual aesthetics and detail.}
        \resumeItem{Produced high-quality 3D environments, props, characters, and VFX in Blender and Substance Painter, collaborating closely with game designers and developers to translate concepts into game-ready assets.}
        \resumeItem{Led 3D art and technical implementation for Aku Si Juragan Empang (3.5 million downloads), building the full Unity scene including UI systems, character rigs with blend shapes, environment props, and shader-based effects.}
        \resumeItem{Constructed a cinematic open-world environment for Mount Nirwana on Roblox (7 million visits) with terrain sculpting, foliage instancing, and dynamic environment lighting.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelance Technical Artist and 3D Artist}{February 2025 -- Present}
      {Fiverr}{Remote}
      \resumeItemListStart
        \resumeItem{Implemented 3D and 2D art assets into client Unity projects, resolving visual bugs and technical issues during asset integration while maintaining the artist's original vision throughout.}
        \resumeItem{Built and optimized UI layouts and particle effects in Unity for 5 gamification prototypes within two-week sprint cycles, reducing load times by 25 percent through targeted asset optimization.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Game UI and Design System Pipeline} $|$ \emph{Unity, Canvas, Animator, Photoshop, Figma}}{2022 -- 2024}
          \resumeItemListStart
            \resumeItem{Designed and implemented complete UI systems for 35 shipped games, covering wireframing, user flow mapping, design system creation, and full Unity Canvas implementation with animations and tweens.}
            \resumeItem{Built reusable UI component libraries in Unity with Animator-driven transitions, reducing UI implementation time by 60 percent across multiple titles with different visual styles.}
            \resumeItem{Created Particle System-based UI feedback effects and Shader Graph-driven animated backgrounds and UI shaders, enhancing visual polish and player interaction feedback.}
            \resumeItem{Collaborated directly with developers, providing constructive feedback during design reviews and iterating rapidly on visual and technical issues found during QA testing.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{BatchProcessPro Blender Add-on} $|$ \emph{Python, Blender API, Unity Integration}}{2024}
          \resumeItemListStart
            \resumeItem{Developed a custom Blender production tool automating retopology, PBR texture baking, LOD generation, and FBX export directly compatible with Unity HDRP, URP, and standard pipelines, reducing asset production time by 90 percent.}
            \resumeItem{Built an Auto Bake module for 6 PBR map types with automatic cage creation and Unity-ready material setup, eliminating manual texture configuration steps during asset implementation.}
            \resumeItem{Introduced Mask Map channel packing tools compatible with Unity HDRP and URP Lit shaders, streamlining the technical handoff between Blender and Unity.}
            \resumeItem{Expanded the Auto LOD generator with customizable polygon reduction ratios and optional collider generation, supporting mobile and console game engine optimization requirements.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Modular Character System and Pipeline} $|$ \emph{Blender, Unity, Substance Painter, Python}}{2024}
          \resumeItemListStart
            \resumeItem{Architected a modular character system with swappable body parts, enabling rapid generation of 100 unique character variations fully implemented into Unity with correct LOD, materials, and rigs.}
            \resumeItem{Applied atlas texturing across all character variants, packing material zones into single texture atlases to reduce per-character draw calls and rendering cost by 45 percent on mobile devices.}
            \resumeItem{Built a Blender Python add-on automating character variant generation with LOD-aware toggling, reducing character setup time by 80 percent and eliminating manual Unity import steps.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Unity (Art Implementation):}{ Canvas UI Layout, Animator, UI Animation and Tweens, Particle System, Shader Graph, Prefab System, Asset Management, Scene Organization, Visual Bug Fixing} \\
     \textbf{Unity C\# Scripting:}{ Editor Scripting, Custom Inspector Tools, Component Modification, Asset Pipeline Scripting, Automated Import Workflows} \\
     \textbf{UI and UX Design:}{ UI Design, UX Design, User Flow, Wireframing, Design Systems, Prototyping, Visual Consistency, Interaction Design} \\
     \textbf{3D Tools:}{ Blender (Advanced), Substance Painter, Substance Designer, Low-Poly Modeling, High-Poly Modeling, Retopology, Rigging, Animation, Props, Characters, Environments, VFX} \\
     \textbf{Texturing and Materials:}{ Photoshop (Advanced), Texture Painting, UV Mapping, Atlas Texturing, PBR Workflows, Hand-Painted Textures, Shader Graph, Texture Compression} \\
     \textbf{Optimization and Performance:}{ LOD Generation, Draw Call Batching, Occlusion Culling, Texture Streaming, Polygon Budget Management, Mobile Performance Profiling, GPU Profiling} \\
     \textbf{Game Engines:}{ Unity 2D and 3D, Unity HDRP and URP, Unreal Engine 5, Roblox Studio} \\
     \textbf{Pipeline and Tooling:}{ Python, Blender Add-on Development, Unity Editor Scripting, Automated Workflows, FBX Export, GLTF Export, Git, GitHub} \\
     \textbf{Collaboration:}{ Cross-Functional Teamwork, Constructive Feedback, Art Direction Communication, Production Schedule Management, Quality Checks}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
