%-------------------------
% ATS-Optimized Resume for Ardi Rudini
% Tailored for: 3D Artist / Level Designer / Game Developer / Technical Artist
% Based off of: https://github.com/sb2nov/resume (Jake Gutierrez template)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ardi Rudini} \\ \vspace{1pt}
    \small +6285659001753 $|$ \href{mailto:ardirdeveloper@gmail.com}{\underline{ardirdeveloper@gmail.com}} $|$
    \href{https://www.linkedin.com/in/ardirdn/}{\underline{linkedin.com/in/ardirdn}} $|$
    \href{https://ardigamedev.com/}{\underline{ardigamedev.com}}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
  \small{
    Results-driven 3D Artist and Game Developer with 7+ years of hands-on experience founding and leading a game studio that shipped 35+ titles across Mobile and Roblox platforms, collectively achieving 15 million+ downloads and visits. Proven expertise in 3D modeling, level design, environment art, technical art, and full-cycle game production. Skilled in Blender, Unity, Unreal Engine, and Roblox Studio, with a strong foundation in Python and C\# tool development. Passionate about creating visually compelling game worlds and building production tools that accelerate asset pipelines.
  }


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universitas Pembangunan Nasional Veteran Jakarta}{Jakarta, Indonesia}
      {Bachelor of Informatics}{Sep. 2019 -- Jul. 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Founder, Lead 3D Artist \& Game Developer}{Sep. 2017 -- Present}
      {Trimatra Studio}{West Java, Indonesia}
      \resumeItemListStart
        \resumeItem{Founded and grew an indie game studio from 2 to 8 members, shipping 35+ titles across Google Play and Roblox platforms with a combined reach of 15 million+ downloads and visits.}
        \resumeItem{Led 3D art direction for ``Aku Si Juragan Empang,'' a mobile simulation game achieving 3.5 million+ downloads by creating all 3D environments, characters, and props using Blender with atlas texturing and modular asset workflows.}
        \resumeItem{Designed and built the open-world environment for ``Mount Nirwana'' (Roblox), a cinematic mountain adventure that garnered 7 million+ visits, utilizing custom terrain sculpting, atmospheric lighting, and optimized draw-call batching for 50+ concurrent players.}
        \resumeItem{Created all 3D assets, level layouts, and UI/UX designs for ``Aku Si Juragan Kosan,'' securing 500K+ downloads within 3 months of launch through polished visual quality and intuitive game design.}
        \resumeItem{Prototyped 30+ hyper-casual game concepts in partnership with Voodoo, soft-launching ``Beauty Race'' (500K+ downloads) after iterating through rapid CPI testing and visual optimization cycles.}
        \resumeItem{Designed and developed 5+ Roblox experiences for RIVRS partnership, accumulating 1 million+ total visits by creating immersive 3D environments with Roblox Studio and custom Lua scripting.}
        \resumeItem{Architected backend systems using Firebase to support 10,000+ daily active users, handling real-time data synchronization, user authentication, and in-app purchase transactions with 99.9\% uptime.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelance Game Developer \& 3D Artist}{Feb. 2025 -- Present}
      {Fiverr}{Remote}
      \resumeItemListStart
        \resumeItem{Designed and developed a corporate metaverse experience on Roblox, integrating a custom reward system that increased client engagement by 20\% and drove a 15\% uplift in loyalty point utilization during the pilot phase.}
        \resumeItem{Led R\&D on 5+ gamification mechanics for a banking client, selecting the top 2 strategies to modernize digital banking interfaces and improve user retention by 12\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{BatchProcessPro -- Blender Production Pipeline Add-on} $|$ \emph{Python, Blender API}}{2024}
          \resumeItemListStart
            \resumeItem{Developed a comprehensive Blender add-on that automates retopology, PBR texture baking, LOD generation, multi-view rendering, and batch export, reducing per-asset processing time from 30+ minutes to under 3 minutes.}
            \resumeItem{Engineered Auto Bake module: automated high-poly to low-poly texture transfer for 6 PBR map types (Diffuse, Normal, Roughness, AO, Metallic, Height) with automatic cage creation and complete Principled BSDF shader node wiring.}
            \resumeItem{Built Auto Render module: generates multi-angle renders (Single, 3-View, 4-View Grid, Turntable) across 7+ shading modes with a single click, supporting batch operations on entire asset libraries.}
            \resumeItem{Implemented Mask Map Tools for channel packing/unpacking compatible with Unity HDRP/URP and Unreal Engine ORM formats.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Level Design Portfolio -- Multi-Engine Environments} $|$ \emph{Unreal Engine, Unity, Roblox Studio}}{2022 -- 2024}
          \resumeItemListStart
            \resumeItem{Designed and built 12+ complete environment scenes across Unreal Engine, Unity, and Roblox Studio, ranging from realistic South East Asian villages to stylized toon cities, demonstrating versatility in both realistic and stylized art directions.}
            \resumeItem{Created cinematic lighting setups, terrain sculpting, and post-processing stacks in Unreal Engine for photorealistic abandoned village and temple environments using Landscape Tools, Lumen, and Material Editor.}
            \resumeItem{Developed stylized environments in Unity with ProBuilder, Terrain Tools, Post-Processing, Cinemachine, and Timeline for in-game cinematics.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Modular Character System} $|$ \emph{Blender, Python, Atlas Texturing}}{2024}
          \resumeItemListStart
            \resumeItem{Designed a modular character pipeline supporting hot-swappable heads, hair, shirts, pants, and shoes with automatic body-part visibility management, enabling rapid generation of 100+ unique character variations.}
            \resumeItem{Built a custom Blender randomizer add-on in Python that automates character variant generation with LOD-aware visibility toggling, reducing character setup time by 80\%.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Deketin -- Student Assignment Platform} $|$ \emph{React, Firebase, Google OAuth 2.0}}{2023}
          \resumeItemListStart
            \resumeItem{Architected a ``Tinder-style'' matchmaking web application with programmatic routing across 5+ modules (Card Swiping, Chat, Settings), achieving less than 2-second load times using React lazy loading.}
            \resumeItem{Deployed Firebase Realtime Database for a zero-latency messaging system, synchronizing chat states with less than 100ms latency and protecting 7+ private routes with Google OAuth 2.0 authentication.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{3D Modeling \& Texturing}{: Blender (Advanced), Maya, 3ds Max, Substance Painter, Adobe Illustrator, Atlas Texturing, Modular Asset Creation, PBR Workflows} \\
     \textbf{Game Engines}{: Unity (2D/3D), Unreal Engine, Roblox Studio} \\
     \textbf{Level Design \& Environment Art}{: Terrain Sculpting, Lighting \& Atmosphere, Scene Optimization, ProBuilder, Landscape Tools, Post-Processing, Cinemachine, Timeline, Lumen, Material Editor, Sequencer, Blueprints} \\
     \textbf{Programming \& Scripting}{: Python (Blender/Maya Plugins), C\# (Unity Tools \& Editor Scripting), Lua (Roblox), JavaScript, React} \\
     \textbf{Pipeline \& Production}{: Git/GitHub, Perforce, Firebase, LOD Generation, Texture Baking, Retopology, UV Unwrapping, Rigging} \\
     \textbf{UI/UX Design}{: Game UI Design, Adobe Illustrator, Figma, Mobile-First Design}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
