%-------------------------
% ATS-Optimized Resume — Level Designer Focus
% Ardi Rudini
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ardi Rudini} \\ \vspace{1pt}
    \small +6285659001753 $|$ \href{mailto:ardirdeveloper@gmail.com}{\underline{ardirdeveloper@gmail.com}} $|$
    \href{https://www.linkedin.com/in/ardirdn/}{\underline{linkedin.com/in/ardirdn}} $|$
    \href{https://ardigamedev.com/}{\underline{ardigamedev.com}}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
  \small{
    Creative Level Designer and Environment Artist with 7+ years of experience designing, building, and polishing game environments across Unreal Engine, Unity, and Roblox Studio. Led art and design direction for 35+ shipped titles with a combined 15 million+ downloads and visits, personally designing world layouts, gameplay flow, lighting atmospheres, and environmental storytelling for mobile, PC, and Roblox platforms. Portfolio includes 12+ complete environment showcases ranging from photorealistic abandoned villages (Unreal Engine) to stylized toon cities (Unity) and cinematic mountain landscapes (Roblox). Strong foundation in 3D asset creation, terrain sculpting, and scene optimization for real-time performance.
  }


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universitas Pembangunan Nasional Veteran Jakarta}{Jakarta, Indonesia}
      {Bachelor of Informatics}{Sep. 2019 -- Jul. 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Founder, Lead Level Designer \& Environment Artist}{Sep. 2017 -- Present}
      {Trimatra Studio}{West Java, Indonesia}
      \resumeItemListStart
        \resumeItem{Designed world layouts, gameplay flow, and environmental storytelling for 35+ shipped game titles across Google Play and Roblox, defining player pathing, pacing, and spatial composition for each project.}
        \resumeItem{Architected the open-world mountain environment for ``Mount Nirwana'' (Roblox, 7M+ visits): designed multi-route hiking paths with skill-based shortcuts, elevation-driven pacing, checkpoint placement, and scenic vista reveals to guide player exploration across a 2km+ playable area.}
        \resumeItem{Designed the open-world rainforest environment for ``Mount Halimun'' (Roblox, 3M+ visits): created a hyper-realistic HD recreation of a real-world national park with cooperative carry mechanics, cross-mountain journal systems, and carefully paced encounter zones.}
        \resumeItem{Led level design for ``Aku Si Juragan Empang'' (3.5M+ downloads): designed the fish pond simulation space with intuitive NPC routing, player-facing zone hierarchy (shop, pond, service areas), and progressive unlockable areas that drove 30+ minute average session times.}
        \resumeItem{Crafted 3D environments for ``Aku Si Juragan Kosan'' (500K+ downloads): designed a multi-floor boarding house with functional room layouts, tenant pathfinding zones, and expandable building modules that supported the upgrade-driven gameplay loop.}
        \resumeItem{Designed level blockouts and gameplay spaces for 30+ hyper-casual game prototypes (Voodoo partnership), iterating on spatial layouts and obstacle placement to optimize player engagement metrics during CPI testing.}
        \resumeItem{Optimized all environments for real-time performance: implemented draw-call batching, LOD systems, occlusion culling, and atlas texturing to maintain stable frame rates on low-end mobile devices and 50+ concurrent Roblox players.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelance Level Designer \& Environment Artist}{Feb. 2025 -- Present}
      {Fiverr}{Remote}
      \resumeItemListStart
        \resumeItem{Designed and built a corporate metaverse environment on Roblox featuring themed zones, wayfinding systems, and interactive spaces that increased client engagement by 20\% during the pilot phase.}
        \resumeItem{Created 5+ gamified environment prototypes for a banking client, designing spatial layouts that guided users through reward-based interaction flows.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{South East Asian River Village} $|$ \emph{Unreal Engine, Landscape Tools, Lumen}}{2024}
          \resumeItemListStart
            \resumeItem{Designed and built a photorealistic swamp village environment in Unreal Engine 5 featuring traditional South East Asian architecture, lush foliage, water systems, and atmospheric volumetric fog.}
            \resumeItem{Utilized Lumen for dynamic global illumination, Landscape Tools for terrain sculpting, and custom material instances for varied ground surfaces (mud, grass, shallow water).}
            \resumeItem{Produced a cinematic flythrough sequence using Sequencer with 12+ camera angles to showcase environmental storytelling and atmospheric mood progression.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Abandoned Village \& Abandoned Temple} $|$ \emph{Unreal Engine, Unity}}{2024}
          \resumeItemListStart
            \resumeItem{Created two moody, post-apocalyptic environments: an overgrown abandoned village (Unreal Engine) with 17+ cinematic shots, and a mystical ruined temple (Unity) with 19+ carefully composed viewpoints.}
            \resumeItem{Designed environmental storytelling through prop placement, vegetation overgrowth patterns, and lighting contrast zones that guide the player's eye through narrative-driven compositions.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Stylized Toon City \& Toon Seaside City} $|$ \emph{Unity, ProBuilder, Post-Processing}}{2022 -- 2023}
          \resumeItemListStart
            \resumeItem{Designed and built two vibrant cartoon-style city environments featuring colorful modular buildings, playful urban layouts, and seaside architecture with pier and beach areas.}
            \resumeItem{Used ProBuilder for rapid modular geo blockouts, Unity Post-Processing for stylized color grading, and Cinemachine for dynamic in-game camera compositions.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Cinematic Mountain \& Cozy Cafe} $|$ \emph{Roblox Studio}}{2022 -- 2023}
          \resumeItemListStart
            \resumeItem{Designed a dramatic cinematic mountain landscape for Roblox with elevation-based biome transitions, atmospheric haze, and carefully placed scenic overlook points.}
            \resumeItem{Created a cozy cafe interior with functional seating layouts, ambient lighting setups, and warm material choices that establish mood and support social gameplay.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Abandoned Palace \& City Neighborhood} $|$ \emph{Unity, Cinemachine, Timeline}}{2023 -- 2024}
          \resumeItemListStart
            \resumeItem{Built a grand abandoned palace with intricate architectural details and cinematic lighting across 10 composed viewpoints, and a modern urban neighborhood featuring detailed streets and city infrastructure across 20 viewpoints.}
            \resumeItem{Employed Cinemachine for dynamic camera work and Timeline for sequenced environmental storytelling.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Level Design}{: World Layout, Gameplay Flow, Player Pathing, Pacing, Spatial Composition, Blockout/Graybox, Environmental Storytelling, Zone Design, Encounter Design} \\
     \textbf{Unreal Engine}{: Landscape Tools, Lumen, Material Editor, Foliage System, Volumetric Fog, Sequencer, Blueprints, Nanite} \\
     \textbf{Unity}{: ProBuilder, Terrain Tools, Post-Processing, Cinemachine, Timeline, Shader Graph, Lighting Baking} \\
     \textbf{Roblox Studio}{: Terrain Editor, Lighting Properties, Part-Based Construction, Lua Scripting, Atmosphere Objects} \\
     \textbf{3D \& Environment Art}{: Blender (Advanced), Maya, Substance Painter, Atlas Texturing, Modular Asset Creation, PBR Workflows} \\
     \textbf{Optimization}{: LOD Systems, Occlusion Culling, Draw-Call Batching, Texture Atlasing, Mobile GPU Budgeting, Scene Profiling} \\
     \textbf{Version Control}{: Git/GitHub, Perforce, Unity Collaborate}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
