%-------------------------
% ATS-Optimized Resume — UI/UX Designer Focus
% Ardi Rudini
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ardi Rudini} \\ \vspace{1pt}
    \small +6285659001753 $|$ \href{mailto:ardirdeveloper@gmail.com}{\underline{ardirdeveloper@gmail.com}} $|$
    \href{https://www.linkedin.com/in/ardirdn/}{\underline{linkedin.com/in/ardirdn}} $|$
    \href{https://ardigamedev.com/}{\underline{ardigamedev.com}}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
  \small{
    Creative UI/UX Designer with 7+ years of experience designing intuitive, visually polished interfaces for mobile games and web applications that have collectively reached 15 million+ users. Designed complete UI systems — from HUD layouts and menu hierarchies to store interfaces and onboarding flows — for 35+ shipped game titles across Google Play and Roblox. Strong expertise in mobile-first design, game UI/UX conventions, icon design, promotional graphics, and front-end implementation using React and Firebase. Skilled in Adobe Illustrator, Figma, and Blender for creating 2D/3D hybrid visual assets. Focused on user-centered design that maximizes engagement, retention, and monetization KPIs.
  }


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universitas Pembangunan Nasional Veteran Jakarta}{Jakarta, Indonesia}
      {Bachelor of Informatics}{Sep. 2019 -- Jul. 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Founder \& Lead UI/UX Designer}{Sep. 2017 -- Present}
      {Trimatra Studio}{West Java, Indonesia}
      \resumeItemListStart
        \resumeItem{Designed complete UI/UX systems for 35+ shipped game titles across mobile and Roblox platforms, including HUD layouts, menu hierarchies, shop interfaces, settings screens, onboarding flows, and in-game notification systems.}
        \resumeItem{Created the full UI system for ``Aku Si Juragan Empang'' (3.5M+ downloads): designed store UI, inventory management screens, NPC dialogue panels, mission trackers, and economy dashboards with a consistent cartoon-style visual language that contributed to 30+ minute average session times.}
        \resumeItem{Designed promotional graphics and store listing assets for 10+ published games: app icons, featured graphics (1024x500), screenshots with UI overlays, and banner ads — achieving 4.2+ average store ratings through clear visual communication of gameplay value.}
        \resumeItem{Designed UI/UX for ``Juragan Nasi Padang'': created 18+ unique screen layouts (menu, cooking interface, customer queue, upgrade panels) using a warm, food-themed color palette with intuitive touch-friendly interaction patterns.}
        \resumeItem{Created in-game UI for ``Legendary Fish Hunter'' (100K+ downloads): designed fishing HUD, monster battle interface, gear upgrade screens, and location-based map UI with real-time feedback animations.}
        \resumeItem{Designed UI for ``Drop Stack Ball'': produced 30+ unique screen assets including main menu, level selection, in-game HUD, power-up indicators, and reward screens with vibrant, attention-grabbing color schemes optimized for hyper-casual audience retention.}
        \resumeItem{Created all visual branding and UI mockups for ``Detained Souls'': designed dark-themed Discord banners, social media trailer feeds, main menu concepts, and promotional materials that established a cohesive horror-adventure visual identity.}
        \resumeItem{Designed icon systems, button hierarchies, and typography standards across all studio titles, maintaining visual consistency while adapting to each game's unique art direction and target audience.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelance UI/UX Designer \& Game Developer}{Feb. 2025 -- Present}
      {Fiverr}{Remote}
      \resumeItemListStart
        \resumeItem{Designed the interface and user flow for a corporate metaverse experience on Roblox, creating intuitive wayfinding UI and a reward dashboard that increased customer engagement by 20\% and drove 15\% uplift in point utilization.}
        \resumeItem{Led UX research on 5+ gamification mechanics for a banking client, selecting the top 2 strategies based on user engagement data to modernize digital banking interfaces and improve retention by 12\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Game UI/UX Portfolio -- Multi-Title Design System} $|$ \emph{Adobe Illustrator, Figma}}{2019 -- 2024}
          \resumeItemListStart
            \resumeItem{Designed and shipped UI systems across 8+ distinct game brands: Detained Souls (dark horror UI), Drop Stack Ball (vibrant hyper-casual), Juragan Empang (cartoon simulation), Juragan Kosan (management sim), Juragan Nasi Padang (food-themed), Legendary Fish Hunter (adventure RPG), Juragan Fauna (zoo management), and The Death Path (dark action).}
            \resumeItem{Created 100+ unique UI screen layouts spanning genres from simulation to action, including HUDs, menus, shops, inventories, leaderboards, settings, onboarding flows, and contextual pop-ups.}
            \resumeItem{Established game-specific style guides defining color palettes, typography scales, button states (normal/hover/pressed/disabled), icon grids, and spacing systems for each project.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Deketin -- Student Matchmaking Platform} $|$ \emph{React, Firebase, Google OAuth, CSS}}{2023}
          \resumeItemListStart
            \resumeItem{Designed and implemented a ``Tinder-style'' swiping interface with card-based layouts, smooth gesture animations, and programmatic routing across 5+ modules (Swipe, Chat, Profile, Settings, Matches).}
            \resumeItem{Created a real-time chat interface with Firebase Realtime Database, designing message bubbles, read receipts, user presence indicators, and chat list with less than 100ms latency synchronization.}
            \resumeItem{Implemented responsive layouts with mobile-first CSS architecture, ensuring consistent visual quality and interaction patterns across devices.}
            \resumeItem{Designed and integrated a secure authentication flow using Google OAuth 2.0 with persistent session handling across 7+ protected routes.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Personal Portfolio Website} $|$ \emph{React, Vite, CSS, Responsive Design}}{2024 -- 2025}
          \resumeItemListStart
            \resumeItem{Designed and developed a professional portfolio website featuring: interactive game showcase with dynamic filtering, 3D asset gallery with multi-view image grids, level design showcase with engine-based categorization, UI/UX gallery with project-based organization, and tools/add-on detail pages.}
            \resumeItem{Implemented modern UI patterns: scroll-triggered animations (AOS), lazy-loaded image galleries, responsive grid layouts, and dark-themed visual design system.}
            \resumeItem{Optimized all image assets to WebP format with automated conversion pipeline, achieving 60\%+ file size reduction without quality degradation.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Promotional Graphics \& App Store Assets} $|$ \emph{Adobe Illustrator, Photoshop}}{2019 -- 2024}
          \resumeItemListStart
            \resumeItem{Designed app icons, featured graphics, screenshot frames, and banner ads for 10+ published Google Play games, contributing to 4.2+ average store ratings and strong visual CTR.}
            \resumeItem{Created social media content (TikTok thumbnails, Instagram posts, Discord banners) maintaining brand consistency across platforms for studio marketing campaigns.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{UI/UX Design}{: Game UI Design, HUD Design, Menu Systems, User Flow, Wireframing, Prototyping, Mobile-First Design, Responsive Design, Interaction Design, Onboarding Flows, Store Listing Assets} \\
     \textbf{Design Tools}{: Adobe Illustrator (Advanced), Figma, Adobe Photoshop, Canva} \\
     \textbf{Front-End Development}{: React, JavaScript, HTML/CSS, Vite, Responsive Layouts, CSS Animations, AOS} \\
     \textbf{Backend \& Auth}{: Firebase (Realtime Database, Authentication), Google OAuth 2.0, REST APIs} \\
     \textbf{3D \& Visual Assets}{: Blender (Advanced), Substance Painter, 3D UI Elements, Icon Rendering} \\
     \textbf{Game Engines}{: Unity (UI Toolkit, Canvas), Roblox Studio (ScreenGui, BillboardGui), Unreal Engine (UMG)} \\
     \textbf{Version Control \& Collaboration}{: Git/GitHub, Perforce, Trello, Notion}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
